### 2015-01-14 src/analysis.Rnw
update

>>>>

\begin{table*}[!ht]
\caption*{Selective}
<<results='asis'>>=
print(xtable(s.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection criteria results. }
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Element Scoped}
<<results='asis'>>=
print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The element based sampling criteria results. }
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{N-Selection}
<<results='asis'>>=
print(xtable(s.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Single Operators}
<<results='asis'>>=
print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table*}
